Summary Tables

### 2023-10-16 summary_tables.Rmd
Fix metric per 100k for summary docs/shiny app

for (k in measure) { # loop for ylls or deaths
  for (j in pathway) { # loop for hb or pathway_hb
    for (i in names(io[-c(2,3)])) { # loop for cities

@@

      # Population by age, and age-sex
      pop_by_age <- io[[i]]$demographic %>% group_by(age) %>% 
        summarize(pop_age = sum(population))
      pop_by_age_sex <- io[[i]]$demographic %>% group_by(age, sex) %>% 
        summarize(pop_age_sex = sum(population))

      # get the health burden into the correct format by creating a long format and adding additional columns
      # create long format
      health[[k]][[j]][[i]] <- gather(temp, key = "cause", "measure", 
                                      -sex, -age_cat) %>% 
        mutate(city = i, # create city column
               scenario = case_when( # create scenario column
                 grepl("sc_cycle", cause) ~ get_qualified_scen_name('sc_cycle'),
                 grepl("sc_car", cause) ~ get_qualified_scen_name('sc_car'),
                 grepl("sc_bus", cause) ~ get_qualified_scen_name('sc_bus'),
                 grepl("sc_motorcycle", cause) ~ get_qualified_scen_name('sc_motorcycle')
               ),
               level1 = case_when( # create level 1 column
                 grepl("all_cause", cause) ~ "L1: All Cause",
                 grepl("inj", cause) ~ "L1: RTI"
               ),
               level2 = case_when( # create level 2 column
                 grepl("total_cancer", cause) ~ "L2: Cancer",
                 grepl("CVD", cause) ~ "L2: CVD",
                 grepl("respiratory", cause) ~ "L2: Respiratory",
                 grepl("T2D", cause) ~ "L2: Other",
                 grepl("total_dementia", cause) ~ "L2: Other",
                 grepl("Parkinson", cause) ~ "L2: Other",
                 grepl("inj", cause) ~ "L2: RTI"
               ),
               level3 = case_when( # create level 3 column
                 grepl("IHD", cause) ~ "L3: IHD",
                 grepl("lung_cancer", cause) ~ "L3: lung_cancer",
                 grepl("COPD", cause) ~ "L3: COPD",
                 grepl("stroke", cause) ~ "L3: stroke",
                 grepl("T2D", cause) ~ "L3: T2D",
                 grepl("LRI", cause) ~ "L3: LRI",
                 grepl("breast_cancer", cause) ~ "L3: breast_cancer",
                 grepl("colon_cancer", cause) ~ "L3: colon_cancer",
                 grepl("endo_cancer", cause) ~ "L3: endo_cancer",
                 grepl("liver_cancer", cause) ~ "L3: liver_cancer",
                 grepl("total_dementia", cause) ~ "L3: total_dementia",
                 grepl("myeloma", cause) ~ "L3: myeloma",
                 grepl("myeloid_leukemia", cause) ~ "L3: Myeloid Leukemia",
                 grepl("Parkinson", cause) ~ "L3: Parkinson",
                 grepl("head_neck_cancer", cause) ~ "L3: head_neck_cancer",
                 grepl("stomach_cancer", cause) ~ "L3: stomach_cancer",
                 grepl("inj", cause) ~ "L3: RTI"
               ),
               dose = case_when( # create dose column
                 grepl("_pa_ap_", cause) ~ "PA and AP",
                 grepl("_pa_", cause) ~ "PA",
                 grepl("_ap_", cause) ~ "AP",
                 grepl("_inj", cause) ~ "RTI"
               )
        ) %>% # End mutate 
        # join with demographic information
        left_join(pop_by_age, by = c("age_cat" = "age")) %>%  
        left_join(pop_by_age_sex, by = c("age_cat" = "age", "sex" = "sex")) %>%
        # create new columns showing burden per 100000 people by age or by age and sex
        mutate(metric_100k = measure / pop_age * 100000, 
               metric_100k_sex = measure / pop_age_sex * 100000)

>>>>

for (k in measure) { # loop for ylls or deaths
  for (j in pathway) { # loop for hb or pathway_hb
    for (i in names(io)[!names(io) %in% c('scen_prop','ithim_run' )]) { # loop for cities

@@

      # Total population
      overall_pop <- sum(io[[i]]$demographic$population)

      # get the health burden into the correct format by creating a long format and adding additional columns
      # create long format
      health[[k]][[j]][[i]] <- gather(temp, key = "cause", "measure", 
                                      -sex, -age_cat) %>% 
        mutate(city = i, # create city column
               scenario = case_when( # create scenario column
                 grepl("sc_cycle", cause) ~ get_qualified_scen_name('sc_cycle'),
                 grepl("sc_car", cause) ~ get_qualified_scen_name('sc_car'),
                 grepl("sc_bus", cause) ~ get_qualified_scen_name('sc_bus'),
                 grepl("sc_motorcycle", cause) ~ get_qualified_scen_name('sc_motorcycle')
               ),
               level1 = case_when( # create level 1 column
                 grepl("all_cause", cause) ~ "L1: All Cause",
                 grepl("inj", cause) ~ "L1: RTI"
               ),
               level2 = case_when( # create level 2 column
                 grepl("total_cancer", cause) ~ "L2: Cancer",
                 grepl("CVD", cause) ~ "L2: CVD",
                 grepl("respiratory", cause) ~ "L2: Respiratory",
                 grepl("T2D", cause) ~ "L2: Other",
                 grepl("total_dementia", cause) ~ "L2: Other",
                 grepl("Parkinson", cause) ~ "L2: Other",
                 grepl("inj", cause) ~ "L2: RTI"
               ),
               level3 = case_when( # create level 3 column
                 grepl("IHD", cause) ~ "L3: IHD",
                 grepl("lung_cancer", cause) ~ "L3: lung_cancer",
                 grepl("COPD", cause) ~ "L3: COPD",
                 grepl("stroke", cause) ~ "L3: stroke",
                 grepl("T2D", cause) ~ "L3: T2D",
                 grepl("LRI", cause) ~ "L3: LRI",
                 grepl("breast_cancer", cause) ~ "L3: breast_cancer",
                 grepl("colon_cancer", cause) ~ "L3: colon_cancer",
                 grepl("endo_cancer", cause) ~ "L3: endo_cancer",
                 grepl("liver_cancer", cause) ~ "L3: liver_cancer",
                 grepl("total_dementia", cause) ~ "L3: total_dementia",
                 grepl("myeloma", cause) ~ "L3: myeloma",
                 grepl("myeloid_leukemia", cause) ~ "L3: Myeloid Leukemia",
                 grepl("Parkinson", cause) ~ "L3: Parkinson",
                 grepl("head_neck_cancer", cause) ~ "L3: head_neck_cancer",
                 grepl("stomach_cancer", cause) ~ "L3: stomach_cancer",
                 grepl("inj", cause) ~ "L3: RTI"
               ),
               dose = case_when( # create dose column
                 grepl("_pa_ap_", cause) ~ "PA and AP",
                 grepl("_pa_", cause) ~ "PA",
                 grepl("_ap_", cause) ~ "AP",
                 grepl("_inj", cause) ~ "RTI"
               )
        ) %>% # End mutate 
        # # join with demographic information
        # left_join(pop_by_age, by = c("age_cat" = "age")) %>%  
        # left_join(pop_by_age_sex, by = c("age_cat" = "age", "sex" = "sex")) %>%
        # create new columns showing burden per 100000 people by age or by age and sex
        mutate(metric_100k = measure / overall_pop * 100000, 
               metric_100k_sex = measure / overall_pop * 100000)
